% When generating HTML, use:
%   mkhowto --html --iconserver . --split 4 --link 2 xbel
%
% The catch:
%   You have to be running the version of mkhowto from the Python
%   1.5.2 (post-alpha2) tree, since that's when I added bibtex
%   support.  ;-)

\documentclass{howto}
\usepackage{verbatim}

% define some local macros:
\newcommand{\element}[1]{\texttt{<#1>}}
\newcommand{\attribute}[1]{\texttt{#1}}
\newcommand{\nmtoken}[1]{\texttt{#1}}
\newcommand{\paramentity}[1]{\texttt{\char`\%#1;}}

\newenvironment{longexample}
  {\begingroup\small}
  {\endgroup}

\newcommand{\contributor}[2]{\term{#1 \textnormal{(\email{#2})}}}
\newenvironment{contributorlist}
  {\begin{definitions}}
  {\end{definitions}}


\title{The XML Bookmark Exchange Language}

\author{Fred L. Drake, Jr.}
\authoraddress{
        PythonLabs at Digital Creations \\
        E-mail: \email{fdrake@acm.org}
}

\date{\today}			% XXX update before release!
\release{1.1}
\setshortversion{1.1}

\begin{document}
\maketitle

\begin{abstract}
\noindent
The XML Bookmark Exchange Language (XBEL) is a rich interchange
format for ``bookmark'' data as used by most Internet browsers.  This
document describes the origin of the design, the requirements which
drove the design process, and the resulting document type.
\end{abstract}

\tableofcontents


\section{Introduction
         \label{intro}}

  The XML Bookmark Exchange Language, or XBEL, is an interchange
  format for the hierarchical bookmark data used by current Internet
  browsers.  It is defined as an application of the Extensible Markup
  Language, or XML \cite{w3c-xml}.

  This section descibes the origin of the effort which created the XML
  Bookmark Exchange Language (XBEL), identifies the contributors, and
  provides information on the availability of the public text of the
  DTD and additional documentation on the applications which support
  XBEL.

  \subsection{Origins
              \label{origins}}

    The XML Bookmark Exchange Language is a product of the Python XML
    Special Interest Group (XML-SIG).  The initial intent of the XBEL
    effort was to create a demonstration of XML facilities available
    to Python programmers which would also be useful.

  \subsection{Contributors
              \label{contrib}}

    The initial idea for XBEL was contributed by Mark Hammond.  Mark
    sent his idea to the Python XML-SIG mailing list.  This was closely
    followed by discussions and additional ideas by many of the list
    participants.  The following people contributed to the design of
    the DTD and the related software (listed in alphabetical order by
    last name):

    \begin{contributorlist}
      \contributor{Fred L. Drake, Jr.}{fdrake@acm.org}
        Documentation.  Design input on DTD and the storage of
        metadata.  Implemented direct support for XBEL in Grail.

      \contributor{David Faure}{david@mandrakesoft.com}
        Suggested adding the \attribute{icon} attribute to
        \element{folder} and \element{bookmark} elements, and
        \attribute{icon} to \element{folder}.  Implemented XBEL in the
        Konqueror file manager for the K Desktop Envionment (KDE).

      \contributor{Stefane Fermigier}{fermigie@math.jussieu.fr}
        Modified implementation of software for Internet Explorer
        Favorites conversion using his original Python DOM
        implementation.

      \contributor{Lars Marius Garshol}{larsga@garshol.priv.no}
        Extended the concept to cover all Internet browsers bookmarks
        and came up with the name and acronym.  Implemented support
        for Navigator and Opera bookmark formats.

      \contributor{Geir Ove Gr{\o}nmo}{grove@infotek.no}
        General input on XML and the desired level of complexity.

      \contributor{Marc van Grootel}{bwaumg@urc.tue.nl}
        Design input on the DTD, storage of metadata, and comments on
        the use of XBEL with architectural forms.

      \contributor{Mark Hammond}{MHammond@skippinet.com.au}
        Original concept and DTD for an archival storage format for
        Internet Explorer ``Favorites.''

      \contributor{Jack Jansen}{Jack.Jansen@cwi.nl}
        General input on potential advanced applications.

      \contributor{Andrew M. Kuchling}{akuchling@acm.org}
        Implemented conversion software between XBEL and Lynx
        bookmarks.

      \contributor{Fredrik Lundh}{fredrik@pythonware.com}
        Initial software implementation for Internet Explorer.

      \contributor{Sean McGrath}{digitome@iol.ie}
        General input on XML and document type definitions.

      \contributor{Greg Stein}{gstein@lyra.org}
        General input on XML Namespaces and moderator of complexity.

      \contributor{Walter R. Underwood}{wunder@infoseek.com}
        General input on the use of XML character entites instead of
        adding general entities, and discussion on date/time values in 
        XML.
    \end{contributorlist}

  \subsection{Availability
              \label{availability}}

    Information on XBEL, including the public text and this document,
    is available on the Python XML-SIG Web site at
    \url{http://pyxml.sourceforge.net/topics/xml/xbel/} \cite{xbel-home}.
    Please refer to this Web resource for information on new versions,
    DTD variants, and supporting software.

    The public text for XBEL will be made available through a SOCAT
    catalog at available at:
    \url{http://pyxml.sourceforge.net/topics/xml/dtds/catalog}.  This
    catalog may be used by including a DELEGATE entry in a catalog
    already used by XML processing software.  The DELEGATE entry
    should be:

\begin{verbatim}
DELEGATE "+//IDN python.org" "http://www.python.org/topics/xml/dtds/catalog"
\end{verbatim}


  \subsection{Formal Identification
              \label{formal-ident}}

    The XBEL DTD documented in this report has the Formal Public
    Identifier:

\begin{verbatim}
+//IDN python.org//DTD XML Bookmark Exchange Language 1.1//EN//XML
\end{verbatim}

    Valid instances of this document type may use the following document
    type declaration:

\begin{verbatim}
<!DOCTYPE xbel
  PUBLIC "+//IDN python.org//DTD XML Bookmark Exchange Language 1.1//EN//XML"
         "http://www.python.org/topics/xml/dtds/xbel-1.1.dtd">
\end{verbatim}


\section{Requirements
         \label{requirements}}

  This section describes the functional capabilities which this
  document type supports.  There are three categories of
  functionality supported:  basic bookmark exchange between browsers,
  data storage for advanced Internet resource management tools, and
  simplicity in extending the DTD if needed for specific
  applications.

  \subsection{Relation to Browser Functionality
              \label{req-browser}}

    XBEL instances must be able to describe sufficient data to
    represent the bookmarks of all major Internet browsers.
    It must be possible to convert browser-specific bookmark data to
    XBEL in a lossless manner, though specific conversions may remove
    data for application-specific reasons.  It is especially important
    to consider privacy issues when exchanging bookmark data.

    Conversion from XBEL to a browser-specific format may lose
    information when the data originates from a browser supporting
    bookmark features not available in all browsers.  It is expected
    that software implementing the conversion be able to warn the user
    if conversion will cause the loss of information, as appropriate.

  \subsection{Advanced Application Support
              \label{req-applications}}

    XBEL must be able to support interchange requirements for
    applications not currently implemented as part of typical Internet
    browsers, including (but not limited to!) application-specific
    preference and history information which only pertains to specific
    bookmarks, metadata information, and alternate sources or formats
    for the documents.

    It must be possible for applications to operate on subsets of the
    information stored in an XBEL instance without affecting private
    information stored by other applications.  Application-specific
    data stored in an XBEL instance may be simple text or may be
    heavily structured.

  \subsection{Extensibility
              \label{req-extensibility}}

    Some ability to extend the document type definition is required to 
    encourage reuse of the existing design.  Due to the use of XML,
    only a minimum of inherant flexibility is required, as new
    document types may be formed using namespaces or by allowing the
    use of well-formed but possibly invalid markup \cite{w3c-xml-names}.


\section{XBEL Document Structure
         \label{document-structure}}

  This section describes the structure of XBEL documents.  This
  includes information on each element and attribute defined in the
  DTD.  Some descriptions include references to the parameter entities 
  used to construct the DTD; these are described in Section
  \ref{parameter-entities}, ``Use of Parameter Entities.''

  \subsection{Date/time Attribute Values
              \label{date-time}}

    Several attributes defined in this document type require date/time
    values stored as CDATA.  For these attributes, the value must be
    formatted as an ISO 8601:1988 value containing a date
    \cite{iso8601,iso8601-houston,iso8601-kuhn}.  A time value
    should be supplied whenever the information is available to the
    application which set the value.  The format of the values is
    restricted to the forms specified in the profile defined in
    \emph{Date and Time Formats} \cite{w3c-datetime}.  Attributes
    which require this form of value are described below as having a
    \dfn{date/time value} rather than a CDATA value.

  \subsection{Top-level Information
              \label{top-level}}

    This section describes the top-level element type of XBEL
    documents.

    \subsubsection{The \element{xbel} Element
                   \label{element-xbel}}

      The \element{xbel} element defines the top-level data structure
      stored in an XBEL instance.  It may contain optional
      \element{title}, \element{info}, and \element{desc} elements,
      followed by any number of elements from
      \paramentity{nodes.mix}.  This is similar to the
      \element{folder} element, but it may not be nested and carries
      different attributes.

      \paragraph*{Attributes}
        The \element{xbel} element carries a \attribute{version}
        attribute which has a fixed value that specifies the version
        of the XBEL DTD.  Other attributes indicate the similarity to
        the \element{folder} element.

        \begin{definitions}
          \term{\attribute{version}, \emph{fixed}}
          Fixed value which specifies the version of the DTD in use.

          \term{\attribute{id}}
          ID value to allow linking to this element; only the
          \element{alias} element's \attribute{ref} attribute supports
          a corresponding IDREF value.

          \term{\attribute{added}}
          Date/time value which can be used to record when the
          collection of bookmarks was created.
	\end{definitions}

      \paragraph*{Processing Expectations}
        The \element{xbel} element is in many ways similar to a
        \element{folder} element, but may not be ``folded.''
        Auxillary information, such as an optional \element{title}
        element, may be shown in a substantially different way than
        for \element{folder} in a user interface.

  \subsection{Common Elements
              \label{common-elements}}

    Elements described in this section may occur in different contexts
    within an XBEL instance, but share fundamental semantic
    interpretation in each case.

    \subsubsection{The \element{title} Element
                   \label{element-title}}

      The \element{title} element is used to mark the title associated
      with the immediately enclosing element.  It is used for
      the \element{xbel}, \element{folder}, and \element{bookmark}
      elements.  This element is always optional and may contain
      only character data.

      \paragraph*{Processing Expectations}
        Software which presents bookmark information to the user in
        any form should use the content of this element to identify
        the resource to the user.  Additional information may be
        needed to make the identification unambiguous.

        Applications may use the text of the \element{title}
        during search operations.

      \paragraph*{Rationale}
        Many Internet resources are described by a short title, often
        displayed by the bookmarking facilities.  Storing the title
        allows a significant improvement in user interface
        responsiveness when compared to retrieving the resource to
        reload the title.  Title storage is the approach taken by all
        browsers known to the XBEL designers.

    \subsubsection{The \element{desc} Element
                   \label{element-desc}}

      The \element{desc} element is used to store a human-readable
      description of the enclosing element.  For a \element{folder} or 
      the \element{xbel} element,
      this may be used to more thoroughly explain the subject of the
      bookmarks stored in the collection and why they may be
      interesting.  For a \element{bookmark}, a summary of the
      resource pointed to by the bookmark may be more appropriate.
      This element is always optional and may contain only character
      data.

      \paragraph*{Processing Expectations}
        The content of this element may be displayed to a user
        requesting more information on the folder or bookmark
        containing the description.  In the case of a
        \element{bookmark}, this can be used before actually making a
        request over the network to retrieve the resource.

        Applications may use the text of the \element{desc}
        during search operations.

      \paragraph*{Rationale}
        Many Internet browsers support simple annotation of bookmark
        data with human readable text.  This element is required to
        support exchange of this data.

    \subsubsection{The \element{info} Element
                   \label{element-info}}

      The \element{info} element is used to store metadata related to
      the immediately enclosing element.  The intended use is for
      \element{info} to store a series of \element{metadata} elements,
      each of which ``belongs'' to some application.  An
      ``application'' in this sense may be either a program, such as a
      specific Internet browser, or a more general metadata scheme,
      such as the Dublin Core \cite{dublin-core}.

      The \element{info} element is always optional.  If present, it
      must contain one or more \element{metadata} elements.

      \paragraph*{Processing Expectations}
        Applications are expected to ignore \element{info} elements if
        they are not able to deal with the contents of constituent
        \element{metadata} elements.  Whether or not \element{info}
        elements should be ``passed through'' transparently or removed
        depends on the purpose of the processing application, but an
        effort should be made to retain the information whenever the
        enclosing element is retained, even in a modified form.

      \paragraph*{Rationale}
        This element provides a clean way of isolating
        application-specific metadata from more generally supported
        constructs within the bookmark data.

    \subsubsection{The \element{metadata} Element
                   \label{element-metadata}}

      The \element{metadata} element is used as a container for all
      auxillary information related to a node which belongs to a
      single metadata scheme.  The specific contents of
      \element{metadata} is highly dependent on the metadata scheme
      which applies; XML namespaces should be used to identify
      explicit markup used within the element.

      The DTD for XBEL specifies the content model for
      \element{metadata} as \code{EMPTY}, but any content should be
      considered acceptable so long as the XBEL document is
      well-formed.  The use of \code{EMPTY} avoids making the DTD too
      loose; applications which do not validate need not be
      concerned.  Derivative DTDs can define the parameter entity
      \paramentity{metadata.mix} to be the appropriate content model
      for the application.

      \element{metadata} elements are always optional.  Note that an
      \element{info} element which contains no \element{metadata}
      elements must be removed.

      \paragraph*{Attributes}
        \begin{definitions}
          \term{\attribute{owner}, \emph{required}}
            CDATA value specifies the application which ``owns'' the
            content of the element.  The value of this attribute
            should be a URI which refers to a definition of the
            application and content structure in either human- or
            machine-processible form.  It is not required that the URI
            be addressable through the network.
	\end{definitions}

        It is expected that namespace attributes will be added to
        the element to specify the markup defined for the content of
        the \element{metadata} element.

      \paragraph*{Processing Expectations}
        Within an \element{info} element, each \element{metadata}
        element is required to have a unique value for the
        \attribute{owner} attribute.  Programs which modify the
        contents of \element{metadata} elements should ensure that
        only one \element{metadata} exists for any \attribute{owner}
        value normally modified by the application within affected
        \element{info} elements.  \element{metadata} elements for
        other owners should remain unaffected.

        Specific interpretation of \element{metadata} content is
        highly dependent on both the \attribute{owner} and the
        application, and is not otherwise within the scope of this
        document.

      \paragraph*{Rationale}
        The \element{metadata} element is required to support owner
        identification.  It is entirely reasonable for multiple owners
        of data to share a document type for their information, but
        otherwise require separate processing.  The Resource
        Description Framework provides an example of an approach which
        would require multiple applications to share a namespace
        \cite{w3c-rdf-syntax,w3c-rdf-schema}.  Some additional form of
        ownership identification is required to ensure processors can
        avoid destroying each other's data.

  \subsection{Data Organization
              \label{data-organization}}

    The elements described in this section are used to impose
    organization on a collection of \element{bookmark} nodes.
    \element{folder} is used to support hierarchical organization and
    \element{separator} is used to support non-hierarchical
    organization.

    \subsubsection{The \element{folder} Element
                   \label{element-folder}}

      The \element{folder} element is the element used to support
      hierarchical data organization.  It is the only element type
      which is allowed to nest within itself.

      This element may contain optional \element{title},
      \element{info} and \element{desc} elements.  After this, any
      number of elements from \paramentity{nodes.mix} are allowed.

      \paragraph*{Attributes}
        \begin{definitions}
          \term{\attribute{id}}
          ID value to allow linking to this element; only the
          \element{alias} element's \attribute{ref} attribute supports
          a corresponding IDREF value.

          \term{\attribute{added}}
          Date/time value which records when the folder was added to
          the bookmark collection represented by the instance.

          \term{\attribute{folded}}
          Token which records whether the contents of the folder
          should be displayed by default in a user interface.  The
          value may be \nmtoken{yes} or \nmtoken{no}.

          \term{\attribute{icon}}
          The value of this attribute is a name which identifies an
          icon that the user agent can use to mark the folder for the
          user.  The value must be mapped to an actual icon; is it not
          a URI which points to an image file, since the names should
          (in theory) be usable in multiple user agents which have
          differing capabilities for image display, and may require
          different format or sizes of icon.  Mechanisms to do this
          are outside the scope of this specification.

          \term{\attribute{toolbar}}
          Token which records whether the contents of the folder
          should be used for the ``Personal Toolbar'' provided by some
          user agents.  The value may be \nmtoken{yes} or \nmtoken{no}.
	\end{definitions}

      \paragraph*{Processing Expectations}
        User interfaces should display \element{folder} elements as
        collapsing lists, allowing the user to display or hide the
        contents of the element on demand.  Appropriate behavior
        outside of user interfaces is expected to be application
        specific.

      \paragraph*{Rationale}
        The \element{folder} element may be used to represent
        hierarchical relationships within a collection of bookmarks,
        as deployed in current Internet browsers.
        The \attribute{toolbar} attribute is needed to support the
        ``Personal Toolbar'' information from Netscape Navigator.

    \subsubsection{The \element{separator} Element
                   \label{element-separator}}

      The \element{separator} element can be used to separate
      bookmarks within a collection in a non-hierarchical fashion.  It 
      may be used within a \element{folder} or the \element{xbel}
      element.

      \paragraph*{Processing Expectations}
        The presence of this element may be represented by displaying
        a horizontal line or vertical whitespace in an interactive
        user interface or printed representation.

      \paragraph*{Rationale}
        A simple separator is required to support the bookmark
        structures of existing Internet browsers.

  \subsection{Bookmark Data
              \label{bookmark-data}}

    Only one element type is used to encapsulate information specific
    to an individual bookmark.  No need for alternate elements has
    been demonstrated.

    \subsubsection{The \element{bookmark} Element
                   \label{element-bookmark}}

      A \element{bookmark} element is used to store information about
      a specific resource.  This element may contain the optional
      elements \element{title}, \element{info} and \element{desc}.

      \paragraph*{Attributes}
        The \element{bookmark} element carries more attributes than
        other elements defined in XBEL.  These attributes are used to
        carry much of the common information maintained on bookmarks
        by the major browsers.

        \begin{definitions}
          \term{\attribute{href}, \emph{required}}
          URI which specifies the resource described by the
          \element{bookmark} element.

          \term{\attribute{id}}
          ID value to allow linking to this element; only the
          \element{alias} element's \attribute{ref} attribute supports
          a corresponding IDREF value.

          \term{\attribute{icon}}
          This is identical to the \attribute{icon} attribute of the
          \element{folder} element; refer to that description for
          information.

          \term{\attribute{added}}
          Date/time value which indicates when the \element{bookmark}
          element was added to the bookmark collection.

          \term{\attribute{modified}}
          Date/time value which records the time of the
          last known change to the resource identified by the
          \element{bookmark}.

          \term{\attribute{visited}}
          Date/time value which represents the time of the user's last
          ``visit'' to the resource.  Note that the value for
          \attribute{modified} may be more recent than the value for
          \attribute{visited} if software is used that checks for
          resources which have changed since the user last visited the
          resource.  This feature is increasingly common in browsers.
	\end{definitions}

      \paragraph*{Processing Expectations}
        In a user interface, \element{bookmark} should typically be
        represented by the contents of the \element{title} element, if 
        present.  The representation of the bookmark should be
        ``hot,'' allowing traversal to the referenced resource by the
        user.  Additional information on the resource, such as the
        description given in a \element{desc} element, should be
        available to the user on demand.

        Outside a user interface, processing may be too
        application-specific to discuss here.

      \paragraph*{Rationale}
        The use of a single structured element type to represent
        external resources simplifies processing while allowing a rich 
        set of information to be maintained on each resource.

  \subsection{Internal References
              \label{internal-references}}

    A single element is provided to support internal references to
    other elements within an XBEL instance.

    \subsubsection{The \element{alias} Element
                   \label{element-alias}}

      \paragraph*{Attributes}
        Only one attribute is needed for \element{alias}, and is
        required to identify the link referent.

        \begin{definitions}
          \term{\attribute{ref}, \emph{required}}
          IDREF value which refers to a \element{bookmark} or
          \element{folder} element, or the document \element{xbel}
          element.
	\end{definitions}

      \paragraph*{Processing Expectations}
        Software which presents bookmarks in a user interface should
        distinguish aliases from other bookmarks visually, but
        otherwise allow examination of the referent transparently.
        Netscape Navigator does this by presenting the bookmark title
        in an italic font; the appropriate visual distrinction is
        likely to be dependent on other aspects of the user
        interface.

        Outside of user interface considerations, treatment of aliases 
        is application-specific.  However, some guidance may prove
        useful.  When encountering an \element{alias}, an application
        should only need to traverse the \element{alias} and process
        the referent if that referent would not otherwise be
        processed, otherwise, the \element{alias} may usually be
        ignored.  This should become an issue only when the
        application is processing a portion of the bookmark hierarchy
        rather than the complete tree.

      \paragraph*{Rationale}
        Netscape Navigator and Microsoft Internet Explorer bookmarks
        can include ``aliases'' to other nodes in the hierarchical
        structure.  Navigator supports only aliases to bookmark nodes,
        while Internet Explorer also supports aliases to folders.

        Navigator's format simply adds the attribute
        \attribute{aliasid} to nodes which are referred to be aliases,
        and the attribute \attribute{aliasof} to the actual alias.
        All other information is duplicated for each alias of the
        primary bookmark entry.  XBEL uses a distinct element and the
        ID/IDREF mechanism provided by XML to avoid redundency and
        support validation.


\section{DTD Structure
         \label{dtd-structure}}

  This section discusses how the DTD itself is organized.  This is
  mostly of interest to the maintainers of XBEL and any descendent
  document types that may be defined in the future.

  \subsection{Use of Parameter Entities
              \label{parameter-entities}}

    Limited use of parameter entities is made in the XBEL DTD.  The
    suffix-notation is adopted from the ``XMLspec'' DTD report
    \cite{w3c-xmlspec}.  Specifically, the \samp{.mix} suffix is used
    for entities which define repeatable-or groups of elements, and
    \samp{.att} is used for entities which define attributes.

    \subsubsection{The \paramentity{metadata.mix} Entity
                   \label{entity-metadata.mix}}

      

    \subsubsection{The \paramentity{nodes.mix} Entity
                   \label{entity-nodes.mix}}

      The \paramentity{nodes.mix} entity lists the element types which
      may be used to form the nodes of the hierarchical data structure
      described by an XBEL instance.  This entity species a mixture of
      \element{bookmark}, \element{folder}, \element{separator} and
      \element{alias} elements.

    \subsubsection{The \paramentity{node.att} Entity
                   \label{entity-node.att}}

      This entity is used to define attributes for element types which 
      hold the real content of the bookmark data.  It is used on the
      \element{bookmark} and \element{folder} elements.  It defines
      the optional \attribute{added} and \attribute{id} attributes.

    \subsubsection{The \paramentity{url.att} Entity
                   \label{entity-url.att}}

      This entity defines the attributes which are available on
      elements which refer to specific resources.  In XBEL 1.0 and
      1.1, this is only used on the \element{bookmark} element.  It
      defines a required \attribute{href} attribute and the optional
      attributes \attribute{modified} and \attribute{visited}.

  \subsection{Extending the DTD
              \label{extending}}

    Extensibility of XBEL relies on three foundations: XML namespaces
    and the acceptability of well-formed instances, localized
    parameters entities, and the simplicity of the DTD itself.

    The primary expectation for DTD extensions is that new elements
    and attributes will be introduced and defined using XML
    namespaces.  Though still in the stage of a working draft within
    the W3C, namespaces offer the most flexible extension mechanism
    available for XML-based markup languages used in wide-spread
    deployment.  Until validation requirements in the context of
    namespaces are more clearly defined, XBEL instances using
    namespaces can apply well-formedness rules as a vehicle for
    partial validation.

    More traditional document type extension uses parameter entities
    reserved for localization.  The XBEL public text provides three
    such entities as ``hooks'' to allow local customization.  For each 
    of the parameter entities described in Section
    \ref{parameter-entities}, ``Use of Parameter Entities,'' a
    \paramentity{local.\var{name}} variant is declared and used in the 
    definition of each of the entities described above.  This is less
    flexible than the namespace approach, but allows a new document
    type to be created which can be used for validation with current
    tools without having to create a new public text from scratch.

    The third foundation for extensibility, the simplicity of the DTD, 
    can be effectively used only by taking a ``steal this code''
    approach to reuse.  XBEL is sufficiently simple that it can easily 
    be understood in its entirety, and a variant document type created 
    by crafting a new public text.

  \subsection{General Entities
              \label{general-entities}}

    The XBEL DTD defines no general entities.

    \paragraph*{Rationale}
      Since XBEL is intended as an interchange format for software and
      not as an authoring format, there is no need to support typical
      entities used to enter special characters.  Entities which do
      not correspond to Unicode characters are too
      application-specific to predict meaningfully
      \cite{unicode20,unicode21}.


\appendix
\section{Public Text
         \label{public-text}}

  This section contains the entire public text of the XBEL DTD
  corresponding to the Formal Public Identifier presented in Section
  \ref{formal-ident}.  No additional external entities are
  referenced.


\begin{longexample}
\verbatiminput{../xbel.dtd}
\end{longexample}


\nocite{*}
\bibliographystyle{alpha}
\bibliography{xbel}

\end{document}
